Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-06-04 ms.tex
a little more description of spectra in Intro.

\author{Teruyuki Hirano?}
\affiliation{Department of Earth and Planetary Sciences, Tokyo Institute of Technology, Tokyo 152-8550, Japan}

\author{Hajima Kawahara?}
\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan}

@@

\citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.
We also examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to improve the stellar parameters from the data.

>>>>

\author{Teruyuki Hirano}
\affiliation{Department of Earth and Planetary Sciences, Tokyo Institute of Technology, Tokyo 152-8550, Japan}

\author{Hajima Kawahara}
\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan}

@@

\citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore these two hypotheses and see if the the disintegration has returned to the levels found in the Kepler mission.

The high resolution spectrum of \shStar\ \citep{kawahara2013starspots} showed a different temperature and gravity than photometric methods \cite[e.g.][]{brown2011kic}.
\citet{vanlieshout2016kic1255} suggest that one exciting possibility is that gases from the disintegrating planet contaminate the high resolution spectrum.
This would enable compositional and kinematic studies of the disintegrating planet.
Here, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
